Example case study in GMSE

### 2018-08-17 notebook/ms/SI3.Rmd
Reviewer 1 minor comment 2

Simulations using the default GMSE sub-models described above are run using the `gmse` function, which offers a range of options for setting parameter values (see Table 1 for some select examples). Output of `gmse` is an exhaustive list that includes all resources and observations, all stakeholder decisions and actions, and all landscape properties in each time step of the simulation. Results are most easily interpreted visually, so a summary of simulation dynamics is plotted by default (the plot can also be called using the `plot_gmse_results` function, and summaries of results can be obtained using `gmse_summary` and `gmse_table`). An example below shows how simulations are set and interpreted.

@@

|  res_movement   |  20     | Distance (cells) a resource can move in any direction (for movement rules, see res_move_type)    |

@@

|  times_observe  |  1      | For density-based observation (observe_type = 0), landscape subsets viewed during observation    |

@@

\clearpage

>>>>

Simulations using the default GMSE sub-models described above are run using the `gmse` function, which offers a range of options for setting parameter values (see Table 1 for some select examples). Output of `gmse` is an exhaustive list that includes all resources and observations, all stakeholder decisions and actions, and all landscape properties in each time step of the simulation (see [SI7](SI7.pdf) for a description of key data structures). Results are most easily interpreted visually, so a summary of simulation dynamics is plotted by default (the plot can also be called using the `plot_gmse_results` function, and summaries of results can be obtained using `gmse_summary` and `gmse_table`). An example below shows how simulations are set and interpreted.

@@

|  res_movement   |  20     | Distance (cells) a resource can move in any direction (see also res_move_type)                   |

@@

|  times_observe  |  1      | For density-based observation (observe_type = 0), landscape subsets observed                     |

@@
